DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-03-25 scnn.tex
harmonic index => degree

\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{subspace_harmonics_eigenvectors_v2}
	\caption{Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
		%The correspondence is computed in two steps.
		First, we compute the power spectral density (PSD) of each graph eigenvector.
		Second, as there is $2\ell+1$ spherical harmonics for each harmonic index $\ell$, we sum the contributions of the corresponding $2\ell+1$ graph eigenvectors.
		% No real convergence with increasing Nside.
		% Row $j$ is the sum of the (normalized) power spectral densities (PSDs), computed by the SHT, of the $2j+1$ graph Fourier modes $\b u_i$ identified with degree $j$.
		% (\figref{graph_eigenvalues} shows how Fourier modes can be identified to spherical degrees.)
		% The PSD is computed for degrees $\ell=0$ to $\ell = 3 N_{side} -1$.
		% Pixel $k$ in row $j$ measures the energy in frequency band $k$ of the graph Fourier modes identified to be part of band $j$.
		The matrix shows how the subspaces agree: the subspaces spanned by the Fourier modes correspond to those spanned by the spherical harmonics in the low frequencies, and the Fourier modes leak towards adjacent frequency bands at higher frequencies.
		While there is a systematic error, the Fourier modes agree at higher frequencies as $N_{side}$ increases.}
		\label{fig:subspace_harmonics_eigenvectors}
\end{figure}

>>>>

\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{subspace_harmonics_eigenvectors_v2}
	\caption{Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
		%The correspondence is computed in two steps.
		First, we compute the power spectral density (PSD) of each graph eigenvector.
		Second, as there is $2\ell+1$ spherical harmonics for each degree $\ell$, we sum the contributions of the corresponding $2\ell+1$ graph eigenvectors.
		% No real convergence with increasing Nside.
		% Row $j$ is the sum of the (normalized) power spectral densities (PSDs), computed by the SHT, of the $2j+1$ graph Fourier modes $\b u_i$ identified with degree $j$.
		% (\figref{graph_eigenvalues} shows how Fourier modes can be identified to spherical degrees.)
		% The PSD is computed for degrees $\ell=0$ to $\ell = 3 N_{side} -1$.
		% Pixel $k$ in row $j$ measures the energy in frequency band $k$ of the graph Fourier modes identified to be part of band $j$.
		The matrix shows how the subspaces agree: the subspaces spanned by the Fourier modes correspond to those spanned by the spherical harmonics in the low frequencies, and the Fourier modes leak towards adjacent frequency bands at higher frequencies.
		While there is a systematic error, the Fourier modes agree at higher frequencies as $N_{side}$ increases.}
		\label{fig:subspace_harmonics_eigenvectors}
\end{figure}
